---
title: "RMD_cheat_sheet"
author: "Cole Sheeley"
output: html_document
date: "2024-09-19"
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# [***Week 5 RMD Cheat Sheet***]{.underline}

### This code provides examples for future reference on making R markdowns to be uploaded to github

## **Sections** {.tabset}

### YAML settings

YAML is a header that contains the document metadata and explains how to set options like title author and output format (commented out so it doesn't run)

```{r}
# ---
#   title: "example"
#   author: "me"
#   date: "2024-9-19"
#   output: html_document
#   bibiliography: references.bib
# ---
```

### Reading in data and loading libraries

To read data and load libraries in r markdown you need to make a code chunk first. These are siginfied by 3 back ticks (\`) and an {r} which creates the code chunk. Make sure to close the code chunk by another 3 back ticks.

```{r}
# for example lets do a simply dplyr
library(tidyverse)
PSU_fish = read.csv("../data/PSU_Fish_Density.csv") # the .. is shell for going back two directories
head(PSU_fish)
```

### Text formatting and Ordered/numbered lists

To format the text within an R markdown you can easily use the user interface under visual with inserting and format, but heres some short cuts to do it in the source tab

-   Headers: to make a header put a hastag (\#) before writing and it makes it smaller the more (\#) you put

-   Italics: to make a sentence in italics, enclose the words in (\*)

-   bold: similar to italics but two (\*\*) instead of one

-   underline: put ({.underline}) after the words

-   bullet points: use dash marks (-) before the words

-   numbered points:

### Section headers

### Tabsets

### Code chunks

```         
-   with code chunk options (i.e echo = , eval = )
```

### Inserting figures

```         
-   and figure captions
```

### Table outputs

### Inserting Images

### hyperlinks

### Formulas with LaTeX

### Citations

manuscript reference [@wyatt2019]

```{r}
print("Hello!")
```
